Verifying Demonstrations

### 2018-05-25 paper/properties.tex
Edits properties, moves Mallory to conclusions

In our setting, we have three potential adversaries: Alice, Grace and Mallory.
\seb{I changed the name of Grace to Eve to be consistent with the introduction}
\daniel{Changed back to Grace since that's what's in the intro now.}
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 
count but also additionally to deanonymize some of the participants in order to 
arrest them or forcefully convince them to change their minds.
Finally, Mallory represents another nation state and has some interest in 
affecting the stability of Grace's regime, for Mallory's own gain, thus 
supporting either Grace or Alice as she see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
\seb{we have to justify why Mallory is not captured either by Alice or Grace}
In addition, Mallory could also have simply as her objective to cause a 
denial-of-service attack on the architecture of \PRIVO.
In the following two subsections, we will formally define some security 
properties specifying the computational effort needed by the adversaries to 
succeed.

@@

Note that in general terms, protesting is very similar to petitions, which in 
turn are similar to voting: all three situations correspond to many individuals 
expressing their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting. 
To draw on this analogy, afterwards we will discuss the relationship between voting and protesting when categorizing the security requirements into verifiability and privacy properties.

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability:] every voter can verify that their vote is 
    included in the result.
\end{description}
We translate the votes into \emph{participation proofs}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

To define these properties more formally in the context of protest, we desire three verifiability requirements, among which eligibility can be further broken up in four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}:
    anyone can verify that each participation proof provides temporal and 
    spatial eligibility and that only one participation proof is counted per 
    individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}:
      prove that the proof was created after the start of the protest and
      before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}:
      prove that the proof is spatially related to the physical location or 
      journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}:
      prove that no individual can be counted more than once for a particular 
      protest.
    \item\label{DesignatedEvent} \emph{Designated event}:
      prove that the proof is designated for the protest.
    \end{requirements}

@@

In addition to the verification requirements, we also need to formalize the privacy properties.
As we indirectly pointed out earlier, we focus on the privacy provided to Alice and the protesters.
In particular, our objective is that as long as Alice can conceal her identity 
at the demonstration and escape without arrest, her support is recorded in the 
data without her privacy being violated.
\seb{I think this sentence should be clarified}

In voting protocols, there are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
\item[Vote privacy:] the voting does not reveal any individual vote.
\item\label[Receipt freeness:] the voting system does not provide any data that 
  can be used as a proof of how the voter voted.
\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the 
  vote was cast in any particular way.
\end{description}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion 
resistance implies receipt freeness, which in turn implies vote privacy.
Coercion resistance is probably not possible to achieve for protests:
\eg Grace can simply physically bring Alice to a protest against her will.

@@

This leaves us with what should correspond to vote privacy.
We need unlinkability between Alice's identity and Alice's participation proof.
Given a participation proof, Grace will not be able to tell if it belongs to 
Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice's, she should not 
be able to link another proof as a consequence.
Hence, we can summarize our needed properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} Participants must be unlinkable to their proofs.
\item\label{ProtestUnlink} Participants (or proofs for the same participant) 
  must be unlinkable between different protests.
\end{requirements}
Thus Alice can always argue to be part of the protest in Grace's favour instead 
of any protest against Grace, which, in fact, is a slight increase in privacy 
over ordinary protests.

>>>>

In our setting, we have two potential adversaries: Alice and Grace.
\seb{I changed the name of Grace to Eve to be consistent with the introduction}
\daniel{Changed back to Grace since that's what's in the intro now.}
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 
count but also additionally to deanonymize some of the participants in order to 
arrest them or forcefully convince them to change their minds.
In the following two subsections, we will define the desired security 
properties.

@@

We note that, in general terms, protesting is very similar to petitions, which 
in turn are similar to voting: all three situations correspond to many 
individuals expressing their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or 
persecution), hence we desire to have similar properties of verification and 
privacy for verifying a protest as there are for voting.

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability:] every voter can verify that their vote is 
    included in the result.
\end{description}
We translate the votes into \emph{participation proofs}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility 
requirement must include temporal and spatial eligibility (\ie each 
participation proof satisfies some temporal and spatial relation to the 
protest).
In essence, the proof must bind the person to the time and location of the protest.

To define these properties more formally in the context of protest, we desire 
three verifiability requirements, among which eligibility can be further broken 
up into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}:
    anyone can verify that each participation proof provides temporal and 
    spatial eligibility and that only one participation proof is counted per 
    individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}:
      prove that the proof was created after the start of the protest and
      before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}:
      prove that the proof is spatially related to the physical location or 
      journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}:
      prove that no individual can be counted more than once for a particular 
      protest.
    \item\label{DesignatedEvent} \emph{Designated event}:
      prove that the proof is designated for the protest.
    \end{requirements}

@@

In addition to the verification requirements, we also need to define the 
privacy properties.
In voting protocols, there are also three levels of 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
\item[Vote privacy:] the voting does not reveal any individual vote.
\item[Receipt freeness:] the voting system does not provide any data that can 
  be used as a proof of how the voter voted.
\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the 
  vote was cast in any particular way.
\end{description}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion 
resistance implies receipt freeness, which in turn implies vote privacy.
Coercion resistance is probably not possible to achieve for protests:
\eg Grace can simply physically bring Alice to a protest against her will.

@@

This leaves us with what should correspond to vote privacy.
We need unlinkability between Alice's long-term identity and Alice's 
participation proof.
Given a participation proof, Grace will not be able to tell if it belongs to 
Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice's, she should not 
be able to link another proof as a consequence.
Hence, we can summarize our needed properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} Participants must be unlinkable to their proofs.
\item\label{ProtestUnlink} Participants (or proofs for the same participant) 
  must be unlinkable between different protests.
\end{requirements}
Thus Alice can always argue to be part of the protest in Grace's favour instead 
of any protest against Grace, which, in fact, is a slight increase in privacy 
over ordinary protests.
